Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-01 paper/ms.tex
update manuscript

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
    pixel cutout}, with a logarithmic grayscale\added{ showing the
    flux in each pixel}. The yellow star is
    the position of \tn.  White circles are resolved Gaia sources with
    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
    being larger}.  The black \texttt{X} and white \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. \replaced{Dashed lines of constant declination
    and right ascension are shown}{The compass shows cardinal
    directions in celestial coordinates. Dashed lines of constant
    declination are separated by 1$'$, while those of right ascension
    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible sources of the
    transits.
		\label{fig:scene}
	}
\end{figure}

@@

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines was found. To set limits on the contributions of a close-by
star to the observed spectrum, we injected a second set of lines to
the mean least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$. The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.

@@

In ``Method 1'', we measured spectroscopic parameters from each of the
CHIRON spectra (Section~\ref{subsec:chiron}).  We then calculated the
stellar radius and reddening following \citet{stassun_accurate_2017}.
We first derived the bolometric flux by combining available broadband
magnitudes from Gaia, Tycho-2, APASS, 2MASS, and WISE.  We then fitted
the SED with the \citet{kurucz_atlas12_2013} stellar atmopshere
models, and summed to find $F_{\rm bol}$.  When fitting the atmosphere
model, we varied the extinction ($A_{\rm V}$) and the overall
normalization.  This procedure yielded $A_{\rm V} = 0.20\pm0.03$,
which agrees with the average from the \cn\ isochrone fits of
\citet{randich_gaiaeso_2018}.  Combining the spectroscopic effective
temperature, bolometric flux, and Gaia distance, we determined the
stellar radius using the Stefan-Boltzmann law.  Combining this radius
with the spectroscopic $\log g$ also yields a stellar mass.

In ``Method 2'', we simply used the observed location of \tn\ in the
HR diagram and interpolated against the 40$\,$Myr isochrone.  This
method leverages the relative location of \tn\ within the narrow \cn\
isochrone to derive precise, theoretically self-consistent constraints
on all of the stellar parameters.  Although this approach would fail
for a low-mass star, \tn\ is above the stellar masses where the Gaia
photometry and isochrone models begin to diverge.

Method 1 yielded a stellar mass that seemed to be high relative to the
observed CHIRON effective temperature ($1.21 M_\odot$ to $5946\,{\rm
K}$, with relative uncertainties of a few percent on each). To avoid
poorly understood systematics,  we adopted the stellar parameters from
Method 2, and report them in Table~\ref{tab:starparams}.

@@

We fitted the model using \texttt{PyMC3}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the exoplanet
transit, we used the \texttt{exoplanet} code
\citep{exoplanet:exoplanet}.  After initializing each model with the
parameters of the maximum {\it a posteriori} model, we assumed a
Gaussian likelihood, and sampled using \texttt{PyMC3}'s gradient-based
No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}. We used $\hat{R}$ as
our convergence diagnostic \citep{gelman_inference_1992}.

@@

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's \replaced{contraction and
photoevaporation}{composition and therefore future atmospheric
evolution}.  If an RV campaign were timed to coincide with TESS
Sectors 36 and 37 (3 March 2021 through 28 April 2021), it would
significantly ease extraction of the Keplerian signal.  The reason is
that the RVs, activity indicators, and photometry could be modeled
simultaneously \citep[{\it
e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.  Combining
photometric and radial velocity data from non-overlapping epochs would
also constrain the models, but perhaps not quite as convincingly.

While we hope that RV observations will be pursued, data acquired
during the TESS mission extension may also help in understanding the
system \citep{bouma_extend_2017,huang_expected_2018}.  Any
misalignment between the star's spin axis and the planet's orbit
should induce nodal precession, which could yield large changes in the
transit duration given the system's high impact parameter.  If
observed, this could be a spectroscopy-free method for confirming the
planet.

@@

\added{The authors are grateful to the anonymous referee for their
constructive comments and suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
    pixel cutout}, with a logarithmic grayscale\added{ indicating the
    flux in each pixel}. The yellow star is
    the position of \tn.  White circles are resolved Gaia sources with
    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
    being larger}.  The black \texttt{X} and white \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. \replaced{Dashed lines of constant declination
    and right ascension are shown}{The compass shows cardinal
    directions in celestial coordinates. Dashed lines of constant
    declination are separated by 1$'$, while those of right ascension
    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible sources of the
    transits.
		\label{fig:scene}
	}
\end{figure}

@@

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines was found. To set limits on the contributions of a close-by star
to the observed spectrum, we injected a \replaced{second set of lines
to the mean least-squares deconvolution profile}{secondary signal into
the mean least-squares deconvolution profile} derived from the CHIRON
observations.  The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$.  The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.
\added{
  We verified these results by injecting secondary lines directly into
  the spectrum and then deriving its LSD broadening profile as we
  would for a normal observation.  The results were nearly identical,
  save for greater computational cost.
}

@@

\explain{NOTE: the description of why we avoided Method 1 has been moved
from a paragraph at the end of this section, to the paragraph below.}

In ``Method 1'', we measured spectroscopic parameters from each of the
CHIRON spectra (Section~\ref{subsec:chiron}).  We then calculated the
stellar radius and reddening following \citet{stassun_accurate_2017}.
We first derived the bolometric flux by combining available broadband
magnitudes from Gaia, Tycho-2, APASS, 2MASS, and WISE.  We then fitted
the SED with the \citet{kurucz_atlas12_2013} stellar atmopshere
models, and summed to find $F_{\rm bol}$.  When fitting the atmosphere
model, we varied the extinction ($A_{\rm V}$) and the overall
normalization.  This procedure yielded $A_{\rm V} = 0.20\pm0.03$,
which agrees with the average from the \cn\ isochrone fits of
\citet{randich_gaiaeso_2018}.  Combining the spectroscopic effective
temperature, bolometric flux, and Gaia distance, we determined the
stellar radius using the Stefan-Boltzmann law.  Combining this radius
with the spectroscopic $\log g$ also yields a stellar mass.
\added{The stellar mass however seemed to be high relative to the
observed CHIRON effective temperature ($1.21 M_\odot$ to $5946\,{\rm
K}$, with relative uncertainties of a few percent on each). We
therefore explored a second method, and ultimately adopted
it because its systematic uncertainties were easier to quantify.}

In ``Method 2'', we \deleted{simply} used the observed location of
\tn\ in the HR diagram and interpolated against the 40$\,$Myr
isochrone.  This method leverages the relative location of \tn\ within
the \deleted{narrow} \cn\ isochrone to derive precise, theoretically
self-consistent constraints on all of the stellar parameters.
Although this approach would fail for a low-mass star, \tn\ is above
the stellar masses where the Gaia photometry and isochrone models
begin to diverge.
\added{
  The statistical uncertainties yielded by this approach are of order
  1\% for the stellar mass and radius.  To quantify the systematic
  uncertainties, we compared the parameters derived from the MIST
  isochrones with those from the
  PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}} isochrones
  \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
  The PARSEC isochrones gave a stellar mass 5\% lower, effective
  temperature 3\% lower, logarithmic surface gravity 1\% lower, and
  radius 8\% lower than the MIST isochrones.  For the sake of
  self-consistency, in Table~\ref{tab:starparams} and the ensuing
  analysis we adopted the stellar
  parameters from MIST.  The reported uncertainties are the quadrature
  sum of the statistical and systematic components.
}

\deleted{
Method 1 yielded a stellar mass that seemed to be high relative to the
observed CHIRON effective temperature ($1.21 M_\odot$ to $5946\,{\rm
K}$, with relative uncertainties of a few percent on each). To avoid
poorly understood systematics,  we adopted the stellar parameters from
Method 2, and report them in Table~\ref{tab:starparams}.
}

@@

We fitted the model\added{s} using \texttt{PyMC3}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the exoplanet
transit, we used the \texttt{exoplanet} code
\citep{exoplanet:exoplanet}.  After initializing each model with the
parameters of the maximum {\it a posteriori} model, we assumed a
Gaussian likelihood, and sampled using \texttt{PyMC3}'s gradient-based
No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}. We used $\hat{R}$ as
our convergence diagnostic \citep{gelman_inference_1992}.

@@

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's \replaced{contraction and
photoevaporation}{composition and future atmospheric
evolution}.  If an RV campaign were timed to coincide with TESS
Sectors 36 and 37 (3 March 2021 through 28 April 2021), it would
significantly ease extraction of the Keplerian signal.  The reason is
that the RVs, activity indicators, and photometry could be modeled
simultaneously \citep[{\it
e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.  Combining
photometric and radial velocity data from non-overlapping epochs would
also constrain the models, but perhaps not quite as convincingly.

While we hope that RV observations will be pursued, data acquired
during the TESS mission extension may also help in understanding the
system \citep{bouma_extend_2017,huang_expected_2018}.  \deleted{Any
misalignment between the star's spin axis and the planet's orbit
should induce nodal precession, which could yield large changes in the
transit duration given the system's high impact parameter.  If
observed, this could be a spectroscopy-free method for confirming the
planet.}
\added{
  In particular, additional photometry will likely enable more
  detailed exploration of whether the orbit of \tn\ is eccentric, and
  also whether the system could host additional transiting planets.
}

@@

\added{The authors thank K.~Anderson for fruitful discussions, and are
grateful to the anonymous referee for their constructive comments and
suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
